Self Regulation Ontology Retest Data: Initial Exploration

### 2017-02-15 SRO_Retest_Analyses.Rmd
cont working on retest exploration

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
sem <- function(x) {sd(x) / sqrt(length(x))}
options(digits = 4)
```

@@

Distribution of Pearson correlations
```{r}
ggplot(cor_df, aes(pearson))+
  geom_histogram()+
  theme_bw()
```

Distribution of spearman correlations
```{r}
ggplot(cor_df, aes(spearman))+
  geom_histogram()+
  theme_bw()
```

@@

Distributions of correlations by task vs. survey
```{r}
cor_df %>%
  gather(key, value, -dv, -task) %>%
  ggplot(aes(value))+
  geom_histogram()+
  theme_bw()+
  facet_wrap(key~task)
```

@@

@@

for(i in 1:length(rest_subs_test_mngf)){
  if(names(rest_subs_test_mngf)[i] == 'sub_id'){
    rest_subs_test_mngf_z$sub_id = rest_subs_test_mngf$sub_id
  }
  else{
    rest_subs_test_mngf_z[,names(rest_subs_test_mngf)[i]] = scale(rest_subs_test_mngf[,i])
  }
}
```

@@

```{r}
library(psych)
corMat <- cor(rest_subs_test_mngf_z)
solution <- fa(r = corMat, nfactors = 2, rotate = "oblimin", fm = "pa")
```

Mean reliabilities for different kinds of variables (e.g. drift rates and NDs; separately for EZ and HDDM; subtraction vs basic variables - single vs. multiple)
```{r}
cor_df$dv
```

Distribution of each variable

@@

 Can you get the factor structure for the retest
 step 1:Ttest on all measures of T1 for people w and without retest
 step2 : efa on the people you don't have retest on and then predict how well this holds up for people w retest on t1 and on t2

>>>>

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(lavaan)
library(semTools)
library(psych)
library(GPArotation)
sem <- function(x) {sd(x) / sqrt(length(x))}
options(digits = 4)
```

@@

Distribution of all Pearson correlations
```{r}
ggplot(cor_df, aes(pearson))+
  geom_histogram()+
  theme_bw()
```

Distribution of all Spearman correlations
```{r}
ggplot(cor_df, aes(spearman))+
  geom_histogram()+
  theme_bw()
```

@@

Distributions of correlations by task vs. survey
Task reliability distributions looks alsmost bimodal. Should figure out whether the lower ones are specific tasks or if they are certain kinds of vars (e.g. certain ddm parameters)
```{r}
cor_df %>%
  gather(key, value, -dv, -task) %>%
  ggplot(aes(value))+
  geom_histogram()+
  theme_bw()+
  facet_wrap(key~task)
```

@@

Distribution of each variable
```{r}
#Function to check if the variables that went in to cor_df have normal distributions

diff_from_normal <- function(col){
  return(shapiro.test(col)$p.value < 0.05)
}
```

Check distributions of retest data
```{r}
dist_retest_data <- as.data.frame(apply(retest_data[,matching_dv_columns], 2, diff_from_normal))
names(dist_retest_data) <- c('not_normal')
dist_retest_data$dv <- row.names(dist_retest_data)
row.names(dist_retest_data) <- seq(1:nrow(dist_retest_data))
dist_retest_data = dist_retest_data %>% select(dv, not_normal)
```

Check distributions of test data (for subjects who have retest data - restricting here since there are the subsets of data that went in to the correlation matrix)
```{r}
dist_retest_subs_test_data <- as.data.frame(apply(retest_subs_test_data[,matching_dv_columns], 2, diff_from_normal))
names(dist_retest_subs_test_data) <- c('not_normal')
dist_retest_subs_test_data$dv <- row.names(dist_retest_subs_test_data)
row.names(dist_retest_subs_test_data) <- seq(1:nrow(dist_retest_subs_test_data))
dist_retest_subs_test_data = dist_retest_subs_test_data %>% select(dv, not_normal)
```

What proportion is not normal?
```{r}
sum(dist_retest_data$not_normal)/nrow(dist_retest_data)
```

```{r}
sum(dist_retest_subs_test_data$not_normal)/nrow(dist_retest_subs_test_data)
```

Are the same vars that are not normally distributed in the retest data not normal in test data as well?
List of variables that have different distributions in the two time points (shown here is whether they are normally distributed in the retest data)
A majority of them are drift diffusion parameters (but note that these vars are overrepresented to begin with).
```{r}
dist_retest_data[which(dist_retest_data$not_normal != dist_retest_subs_test_data$not_normal),]
```

Transform non normal vars
Transform both retest and test data if not normally distributed in either. 
Order of transformations tried: log and sqrt
```{r}
transform_dv_df = data.frame(dv = c(), transform = c(), not_normal = c())
#check if normal
diff_from_normal(retest_data[,2])
diff_from_normal(log(retest_data[,2]))
diff_from_normal(sqrt(retest_data[,2]))
#if yes stop and record transformation = none
#if transform: log
#check if normal
#if yes stop and record transformation = log
#if no transform: sqrt

```

Mean reliabilities for different kinds of variables (e.g. drift rates and NDs; separately for EZ and HDDM; subtraction vs basic variables - single vs. multiple)
```{r}
```

--------------------------------

Can you get the factor structure for the retest
step 1:Ttest on all measures of T1 for people w and without retest
```{r}

```

step2 : efa on the people you don't have retest on and then predict how well this holds up for people w retest on t1 and on t2

@@

for(i in 1:length(rest_subs_test_mngf)){
  if(names(rest_subs_test_mngf)[i] == 'sub_id'){
    rest_subs_test_mngf_z$sub_id = rest_subs_test_mngf$sub_id
  }
  else{
    rest_subs_test_mngf_z[,names(rest_subs_test_mngf)[i]] = scale(rest_subs_test_mngf[,i])
  }
}

rest_subs_test_mngf_z <- as.data.frame(rest_subs_test_mngf_z)
```

@@

```{r}
corMat <- rest_subs_test_mngf_z %>% select(-sub_id) %>% cor(.,use = 'complete.obs')

solution <- fa(r = corMat, nfactors = 3, rotate = "oblimin", fm = "pa")
```

```{r}
solution
```

@@
